Robinson et al. 2020 Supplemental Information: Comparing the Radiocarbon and Tree-ring Records for the Upland US Southwest

### 2020-01-19 analysis/paper/paper.Rmd
still trying to get binder working

---
title: "Robinson et al. 2020 Supplemental Information: Comparing the Radiocarbon and Tree-ring Records for the Upland US Southwest"
author:
  - Kyle Bocinsky:
      email: bocinsky@gmail.com
      institute: [CCAC]
      correspondence: true
  - Erick Robinson:
      email: erick.robinson@usu.edu
      institute: [USU]
      correspondence: false
institute:
  - CCAC: Crow Canyon Archaeological Center
  - USU: Utah State University
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::html_document2:
      code_folding: hide
      fig_caption: yes
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks.lua
      - --lua-filter=../templates/pagebreak.lua
    bookdown::pdf_document2:
      fig_caption: yes
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks.lua
      - --lua-filter=../templates/pagebreak.lua
header-includes:
  - \usepackage{subfig}
bibliography: references.bib
csl: "../templates/philosophical-transactions-of-the-royal-society-b.csl" # Insert path for the bib-style
editor_options: 
  chunk_output_type: console
---

>>>>

---
title: "Robinson et al. 2020 Supplemental Information: Comparing the Radiocarbon and Tree-ring Records for the Upland US Southwest"
author:
  - Kyle Bocinsky:
      email: bocinsky@gmail.com
      institute: [CCAC]
      correspondence: true
  - Erick Robinson:
      email: erick.robinson@usu.edu
      institute: [USU]
      correspondence: false
institute:
  - CCAC: Crow Canyon Archaeological Center
  - USU: Utah State University
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::html_document2:
      code_folding: hide
      fig_caption: yes
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks.lua
      - --lua-filter=../templates/pagebreak.lua
bibliography: references.bib
csl: "../templates/philosophical-transactions-of-the-royal-society-b.csl" # Insert path for the bib-style
editor_options: 
  chunk_output_type: console
---
